A significance test for forward stepwise model selection

### 2013-10-09 paper/paper.tex
Moving files, small edits
Expanded forward stepwise section of paper

Before we describe the forward stepwise procedure we require one last
ingredient. To each group of variables we assign a weight $w_g$. These
weights act like penalties or costs, so increasing $w_g$ makes it
\textit{more difficult} for the group $X_g$ to enter the model. The
modeler can choose weights arbitrarily, but we will only use one
particular choice, based on $p_g$, that we discuss later. With this we
are ready to describe the forward stepwise procedure Algorithm \ref{algo:fs}.

\begin{algorithm}
\DontPrintSemicolon
\KwData{An $n$ vector $y$ and $n \times p$ matrix $X$ of $G$ grouped variables}
\KwResult{Active set $A$ of variable groups included in the model}
\SetKwFunction{lsfitResidual}{lsfitResidual}
\caption{Forward stepwise procedure}
\BlankLine
$A \gets \emptyset$\;
$A^c \gets \{ 1, \ldots, G \}$\;
$r_0 \gets y$\;
\For{$counter \leftarrow 1$ \KwTo $\min (n, G)$}{
  $g^* \gets \argmax_{g \in A^c} \norm{X_g^T r_{g-1}}_2 / w_g$\;
  $A \gets A \cup \{ g^* \}$\;
  $A^c \gets A^c \backslash \{ g^* \}$\;
  $r_g \gets $\lsfitResidual{$r_{g-1}, X_{g^*}$}\;
}
\KwRet{$A$}
\label{algo:fs}
\end{algorithm}

@@

@@

\input{../small_sim_results.tex}

@@

\input{../large_sim_results.tex}

>>>>

We allow for the possibility $p > n$ in which case \ref{eq:gmodel} is
generically underdetermined. In such cases it still may be possible to
estimate $\beta$ well if it is sparse--that is, if it has few nonzero
entries \citep{donoho:pursuit}. In the rest of this paper we refer to
variable groups $X_g$ as noise variables if $\beta_g$ is a zero vector
and as true predictor variables if $\beta_g$ has nonzero entries.

Before we describe the forward stepwise procedure we require one last
ingredient. To each group of variables we assign a weight $w_g$. These
weights act like penalties or costs, so increasing $w_g$ makes it
more difficult for the group $X_g$ to enter the model. The
modeler can choose weights arbitrarily, but we will only use one
particular choice, based on $p_g$, that we discuss later. With this we
are ready to describe the forward stepwise procedure, given in Algorithm
\ref{algo:fs}. Note that to prevent saturation, and to enable our p-value
computations, \textit{max.steps} should be at most $\min (n, G) - 1$.

\begin{algorithm}
\DontPrintSemicolon
\KwData{An $n$ vector $y$ and $n \times p$ matrix $X$ of $G$ grouped variables}
\KwResult{Active set $A$ of variable groups included in the model}
\SetKwFunction{lsfitResidual}{lsfitResidual}
\caption{Forward stepwise procedure with groups and weights}
\BlankLine
$A \gets \emptyset$\;
$A^c \gets \{ 1, \ldots, G \}$\;
$r_0 \gets y$\;
\For{$step \leftarrow 1$ \KwTo $max.steps$}{
  $g^* \gets \argmax_{g \in A^c} \norm{X_g^T r_{g-1}}_2 / w_g$\;
  $A \gets A \cup \{ g^* \}$\;
  $A^c \gets A^c \backslash \{ g^* \}$\;
  $r_g \gets $\lsfitResidual{$r_{g-1}, X_{g^*}$}\;
}
\KwRet{$A$}
\label{algo:fs}
\end{algorithm}

@@

Subset selection refers to the problem of choosing a subset of the $p$
potential variables to include in a model. Since there are $2^p$ such
choices, exhaustive search is computationally infeasible when $p$ is
large. If exhaustive search were possible, performing a large
search runs the risk of over-fitting unless model complexity is
appropriately penalized. Algorithm \ref{algo:fs} produces a much
smaller set of potential models, at most \textit{max.steps}. However,
it is a greedy algorithm so the set of models it produces may not
contain the best possible model. This is an inherent shortcoming which
we do not address in this paper.

So far we have left open the question of choosing among the models in
the forward stepwise sequence, i.e. when to stop stepping
forward. Some classical approaches can be posed as optimization
criteria and stop at the step minimizing
\begin{equation}
\begin{aligned}
\label{eq:subsetregress}
\frac{1}{2} \| y - X \beta_s \|_2^2 + \lambda P(\beta_s)
\end{aligned}
\end{equation}
where we have written $\{ \beta_s : s = 1, \ldots, max.steps \}$ as
the sequence of models outputted by forward stepwise. The function
$P(\beta)$ is a penalty on model complexity usually taken to be the
number of nonzero entries of $\beta$. Proposals for $\lambda$ include
2 ($C_p$, AIC \todo{cite}), $\log(n)$ (BIC of \cite{BIC}), and
$2\log(p)$ (RIC of \cite{RIC}). In the current paper we provide
accurate p-values when adding the first noise variable group in the forward
stepwise sequence, and it is natural to consider using these p-values
to choose a model. \cite{sequential:fdr} examined some stopping rules
using the asymptotic p-values of \cite{significance:lasso} and showed
their stopping rules control false discovery rate--the expected
proportion of noise variables among variables declared significant
\citep{fdr}. We explore this further in Section \ref{sec:simulations}.

@@

\input{../small_sim_selection.tex}

\input{../small_sim_estimation.tex}

@@

\input{../large_sim_selection.tex}
